### 2018-10-18 manuscript.rmd
changed palette, color blind friendly but hard to read

ggplot() + 
	scale_x_continuous(name="x") + 
	scale_y_continuous(name="y") +
	geom_rect(data=D, mapping=aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=clade )) + 
	scale_fill_discrete(guide = guide_legend(reverse=TRUE))
```

>>>>

ggplot() + 
	scale_x_continuous(name="x") + 
	scale_y_continuous(name="y") +
	geom_rect(data=D, mapping=aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=clade )) + 
	scale_fill_manual(values = clade_colors, guide = guide_legend(reverse=TRUE))
	#scale_fill_discrete(guide = guide_legend(reverse=TRUE))
```
